Real Time Shape Reconstruction for Near Earth Asteroid Landing

### 2018-03-31 abstract.tex
Starting to describe our algorithm

We assume that the spacecraft contains an initial estimate for the shape of the asteroid.
This shape can be a coarse estimate computed from radar measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid.
This model is defined as a sequence of vertices and triangular facets defined by the vertices.
This shape model is a widely used format for defining three-dimensional shapes in computer applications and has become the standard method for representing asteroid shapes~\cite{neese2004}.

We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid.
This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
Given the time total time of flight the distance can be accurately computed using \( d = \frac{t_f}{2 c} \) where \( c \) is the constant speed of light.
Assuming accurate knowledge of the pointing direction of the spacecraft we can compute a direction from the spacecraft to the measurement location on the surface.
The output of this sensor is a vector, \( \vb{d}_i \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface of the asteroid. 
Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple t transformation
\begin{align*}
    \vb{p}_i = R_A^T R \vb{d}_i .
\end{align*}

Model a lidar on spacecraft which gives vector of the surface in spacecraft fixed frame.

This vector is transformed to the asteroid frame using \( R_A \).

Present algorithm for mesh update

>>>>

We assume that the spacecraft contains an initial estimate for the shape of the asteroid.
This shape can be a coarse estimate computed from radar measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid, such as that shown in~\cref{fig:initial_ellipsoid} which represents the maximum axes for asteroid Castalia.
This model is defined as a sequence of vertices and triangular facets defined by the vertices.
This shape model is a widely used format for defining three-dimensional shapes in computer applications and has become the standard method for representing asteroid shapes~\cite{neese2004}.
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{example-image-golden}
    \caption{Triaxial Ellipsoid Triangular Shape Model~\label{fig:initial_ellipsoid}}
\end{figure}

We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
Given the time total time of flight the distance can be accurately computed using \( d = \frac{t_f}{2 c} \) where \( c \) is the constant speed of light.
Assuming accurate knowledge of the pointing direction of the spacecraft we can compute a direction from the spacecraft to the measurement location on the surface.
The output of this sensor is a vector, \( \vb{d}_i \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface of the asteroid. 
Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple t transformation
\begin{align*}
    \vb{p}_i = R_A^T R \vb{d}_i .
\end{align*}
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{example-image-golden}
    \caption{Simulated LIDAR measurements of asteroid Castalia~\label{fig:lidar_example}}
\end{figure}
Given many measurements, \( \vb{p}_i \), of the asteroid surface we can efficiently update our initial shape estimate to that of the true surface.

Compute angle between measurement and all vertices of shape

Figure out geodesic distance

Update both radius of vertex and weight
